Pillar 2 - Topic Modeling

### 2019-01-16 Pillar 2 - Topic Modeling.Rmd
funciton to prepare LDA reuslts for visualization

## Results
```{r}
prepare_data_LDA_beta <- function(results) tidy(results, matrix = "beta") %>%
                                        mutate(topic = paste("Topic", topic)) %>%
                                          group_by(topic) %>%
                                            top_n(10, beta) %>%
                                          ungroup

prepare_data_LDA_gamma <- function(results, facet = Course){

  data_gamma <- tidy(results, matrix = "gamma") %>%
    mutate(topic = paste("Topic", topic)) %>%
    rename(Code = document) %>%
    left_join(select(d_course, Code, Cluster, Concentration, `Concentration (additional)`), by = "Code")

  if(ensym(facet) == sym("Course")) data_gamma <- data_gamma %>%
                                      rename(facet = Code)

  if(ensym(facet) == sym("Cluster")) data_gamma <- data_gamma %>%
                                       filter(is.na(Cluster)) %>%
                                       rename(facet = Cluster)

  if(ensym(facet) == sym("Concentration")) data_gamma <- data_gamma %>% 
                                             filter(!is.na(Concentration)) %>%
                                             gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
                                             rename(facet = Concentration)

  data_gamma <- data_gamma %>%
    group_by(facet, topic) %>%
      summarise(gamma = mean(gamma)) %>%
    filter(gamma > 0.05)
    ungroup

```{r function visualize_LDA, eval = F}
visualize_LDA_beta <- function(data_prepared, id_plot = "test"){

@@

visualize_LDA_gamma2 <- function(data_prepared, id_plot = "test"){???

@@

```

>>>>

## Results
```{r LDA prepare}
prepare_data_LDA_beta <- function(results) tidy(results, matrix = "beta") %>%
                                        mutate(topic = paste("Topic", topic)) %>%
                                          group_by(topic) %>%
                                            top_n(10, beta) %>%
                                          ungroup %>%
                                          arrange(topic, desc(beta))

prepare_data_LDA_gamma <- function(results, level = Course){

  data_gamma <- tidy(results, matrix = "gamma") %>%
    mutate(topic = paste("Topic", topic)) %>%
    rename(Code = document)

  if(ensym(level) == sym("Course")) data_gamma <- data_gamma %>%
                                      rename(facet = Code)

  if(ensym(level) == sym("Cluster")) data_gamma <- data_gamma %>% 
                                       left_join(select(d_course, Code, Cluster), by = "Code") %>%
                                       filter(!is.na(Cluster)) %>%
                                       rename(facet = Cluster)

  if(ensym(level) == sym("Concentration")) data_gamma <- data_gamma %>%
                                             left_join(select(d_course, Code, Concentration, `Concentration (additional)`), by = "Code") %>%
                                             gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
                                             rename(facet = Concentration)

  data_gamma <- data_gamma %>%
    group_by(facet, topic) %>%
      summarise(gamma = mean(gamma)) %>%
    filter(gamma > 0.05) %>%
    ungroup %>%
    arrange(facet, desc(gamma))

  return(data_gamma)

# Bet Distribution
LDA_description_10 %>% prepare_data_LDA_beta

# Gamma Distribution
LDA_description_10 %>% prepare_data_LDA_gamma(level = Cluster)
```

```{r LDA visualize}
visualize_LDA_beta <- function(data_prepared, id_plot = "test"){

@@

visualize_LDA_gamma2 <- function(data_prepared, id_plot = "test"){

@@
